### 2021-02-24 main.tex
Replace cohomology by homology

\begin{document}	
	\paragraph{Terminology} A \textit{neighborhood} of a point is a set containing an open neighborhood of it.

	\begin{lemma} \label{l: wilder}
		Let $X$ be locally compact and Hausdorff and $Y \subseteq X$ compact. Define the following properties:
		\begin{itemize}
			\item[$(r^n)$] If $K$ and $M$ are compact subsets of $X$ with $\widetilde K = K \cap Y \subset \interior_Y(M \cap Y)$, then $\im r^n_{\widetilde K, M}$ is finite.
			\item[$(r^n_\bullet)$] If $V$ is an open neighborhood of $y \in Y$ there exist another such neighborhood $U \subseteq V$ such that $\im r^n_{U \cap Y, V}$ is finite.
		\end{itemize}
		Then, $(r^{n-1})$ together with $(r^n_\bullet)$ imply $(r^n)$.
	\end{lemma}

	\begin{proof}
		Let $M$ be fixed and let $\sigma$ be the set of compact subsets $K$ with $K \cap Y \subseteq \interior_Y(M \cap Y)$ such that $K$ has a neighborhood $U_K$ in $X$ such that $\im r^n_{U_K \cap Y, M}$ is finite.

@@

		For $i \in \{1, 2\}$ consider $K_i \in \sigma$ and let $K_i^\prime$ and $K_i^\dprime$ be compact neighborhoods of $K_i$ such that
		\begin{equation*}
		K_i \subseteq K_i^\dprime \subseteq \interior K_i^\prime \subseteq K_i^\prime \subseteq U_i,
		\end{equation*}
		where $\im r^n_{U_i \cap Y, M}$ is finite. 
		We can construct such compact neighborhoods using $(\ast)$ as follows:

@@

		Using $\widetilde{K}$ to denote $K \cap Y$ we have the commutative diagram
		\begin{equation*}
		\begin{tikzcd}
		& \arrow[r] \arrow[d] H^n(M) & H^n(M) \oplus H^n(M) \arrow[d] \\
		H^{n-1}(\widetilde K_1^\prime \cap \widetilde K_2^\prime) \arrow[r] \arrow[d] & 
		H^{n}(\widetilde K_1^\prime \cup \widetilde K_2^\prime) \arrow[r] \arrow[d] &
		H^{n}(\widetilde K_1^\prime) \oplus H^n(\widetilde K_2^\prime) \\
		H^{n-1}(\widetilde K_1^\dprime \cap \widetilde K_2^\dprime) \arrow[r] & 
		H^{n}(\widetilde K_1^\dprime \cup \widetilde K_2^\dprime). &
		\end{tikzcd}
		\end{equation*}
		The upper right square has finite image because $\im r^n_{\widetilde K^\prime_i, M}$ is finite. The bottom left square has a finite image using property $(r^{n-1})$. From standard homological algebra using that the middle row is exact, part of the Mayer-Vietoris sequence for the space $\widetilde K_1^\prime \cup \widetilde K_2^\prime$, we conclude that $K = K_1 \cup K_2 \in \sigma$ with open neighborhood $U_K = \interior K^\dprime_1 \cup \interior K^\dprime_2$.

		Let $K$ compact such that $\widetilde K = K \cap Y \subset \interior_Y(M \cap Y)$.
		Consider a finite subset $\{C_1, \dots, C_m\}$ of $\sigma$ such that $Y = \bigcup_{i=1}^m C_i \cap Y$. Here we are using that $Y$ is compact and that any $y \in Y$ has a neighborhood in $\sigma$. Denoting $C = \bigcup_{i=1}^m C_i$ and $D = X \setminus \interior(C)$ we have $K = K \cap C \cup K \cap D$ which imply $K \in \sigma$ since $D \cap Y = \emptyset$ so $D \in \sigma$ trivially.
	\end{proof}

>>>>

\begin{document}	
	We use the following terminology: a \textit{neighborhood} of a point is a set containing an open neighborhood of it.

	The following is a modification of a theorem of Wilder.

	\begin{lemma} \label{l: wilder}
		Let $X$ be locally compact and Hausdorff and $Y \subseteq X$ compact. Define the following properties:
		\begin{itemize}
			\item[$(r^n)$] If $K$ and $M$ are compact subsets of $X$ with $K \cap Y \subset \interior_Y(M \cap Y)$, then $\im H_n\left(K \cap Y \to M\right)$ is finite.
			\item[$(r^n_\bullet)$] If $V$ is an open neighborhood of $y \in Y$, then there exist $U$ an open neighborhood of $y$ contained in $V$ such that $\im H_n\left(U \cap Y \to V\right)$ is finite.
		\end{itemize}
		Then, $(r^{n-1})$ together with $(r^n_\bullet)$ imply $(r^n)$.
	\end{lemma}

	\begin{proof}
		Let $M$ be fixed and let $\sigma$ be the set of compact subsets $K$ with $K \cap Y \subseteq \interior_Y(M \cap Y)$ such that $K$ has a neighborhood $U_K$ in $X$ such that $\im H_n\left(U_K \cap Y \to M\right)$ is finite.

@@

		For $i \in \{1, 2\}$ consider $K_i \in \sigma$ and let $K_i^\prime$ and $K_i^\dprime$ be compact neighborhoods of $K_i$ such that
		\begin{equation*}
		K_i \subseteq K_i^\dprime \subseteq \interior K_i^\prime \subseteq K_i^\prime \subseteq U_i,
		\end{equation*}
		where $\im H_n\left(U_i \cap Y \to M\right)$ is finite. 
		We can construct such compact neighborhoods using $(\ast)$ as follows:

@@

		\begin{equation*}
		\begin{tikzcd}
		& H_n(M) & \arrow[l] H_n(M) \oplus H_n(M) \\
		H_{n-1}(K_1^\prime \cap K_2^\prime \cap Y) & 
		H_{n}((K_1^\prime \cap Y) \cup (K_2^\prime \cap Y)) \arrow[l] \arrow[u] &
		H_{n}(K_1^\prime \cap Y) \oplus H_n(K_2^\prime \cap Y) \arrow[l] \arrow[u] \\
		H_{n-1}(K_1^\dprime \cap K_2^\dprime \cap Y) \arrow[u] & 
		H_{n}((K_1^\dprime \cap Y) \cup (K_2^\dprime \cap Y)) \arrow[l] \arrow[u]. &
		\end{tikzcd}
		\end{equation*}

		The upper right square has finite image because $\im H_n\left(K^\prime_i \cap Y \to M\right)$ is finite for each $i \in \{1, 2\}$. The bottom left square has a finite image using property $(r^{n-1})$. From standard homological algebra (cite Bredon 	Lemma 17.3) using that the middle row is exact, part of the Mayer-Vietoris sequence for the space $(K_1^\prime \cap Y) \cup (K_2^\prime \cap Y) \subseteq Y$, we conclude that $K = K_1 \cup K_2 \in \sigma$ with open neighborhood $U_K = \interior K^\dprime_1 \cup \interior K^\dprime_2$.

		Let $K$ be a compact set such that $\widetilde K = K \cap Y \subset \interior_Y(M \cap Y)$.
		Consider a finite subset $\{C_1, \dots, C_m\}$ of $\sigma$ such that $Y = \bigcup_{i=1}^m C_i \cap Y$. This set can be constructed using that $Y$ is compact and that any $y \in Y$ has a neighborhood in $\sigma$. Denoting $C = \bigcup_{i=1}^m C_i$ and $D = X \setminus \interior(C)$ we have $K = (K \cap C) \cup (K \cap D)$ which imply $K \in \sigma$ since $D \cap Y = \emptyset$ so $K \cap D \in \sigma$ trivially.
	\end{proof}
